Bird beak's elaboration and exploration

### 2021-05-21 Analysis/02-MCMCglmm_mini_chains.Rmd
Update 02-MCMCglmm_mini_chains.Rmd

All the custom code and custom functions called in this document can be downloaded and installed in `R` as the standalone working package `beer` (Beak Elaboration and Exploration in R).
Although `beer` is intentionally designed to be portable and shareable, we advice workers to use it with moderation and tailor it's consumption to their specific research needs.
The following code snippets are used to illustrate the implementation of the functions.
See §§§ for running the actual analyses.

@@

## Loading the data
data(morphdat)

## Loading the trees
data(trees)
```

@@

```{r, parametrise_the_model}
## Set up the parametrising chains models

>>>>

All the custom code and custom functions called in this document can be downloaded and installed in `R` as the standalone working package `beer` (Beak Elaboration and Exploration in R).
Although `beer` is intentionally designed to be portable and shareable, we advice workers to use it with moderation and tailor it's consumption to their specific research needs.
Some analyses in `beer` do take some time to run so we advice to not drive or operate heavy machinery while using it.
Don't use it while driving.
The following code snippets are used to illustrate the implementation of the functions.
See §§§ for running the actual analyses.

@@

## Loading the demo data
data(demo_data)
data(demo_trees)
```

@@

```{r, parametrise_the_model}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = demo_data,
                                   dimensions   = c(1:4),
                                   tree         = demo_trees,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = template,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 10000,
                                       thin   = 100,
                                       burnin = 0))

## Running the three MCMCglmm models
param_chains <- run.mini.chains(param_MCMCglmm, replicates = 3)
```
